User-level Grid Monitoring with Inca 2

### 2007-02-28 papers/hpdc-gmw-2007/paper.tex
reordering of user-level monitoring guidelines and some other minor doc fixes
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6601 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  First, system
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies arise between the resources that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs. 
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

\item In order to reflect regular user experiences, tests or performance
measurements of the Grid infrastructure should be done from a standard user
account.  It is important not to execute from a system administrator's account,
because it may have special privileges and use custom shell initialization files.

\item Also in order to reflect regular user experiences, tests should be
written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.).  This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment, but they should be closely coordinated activities.

@@

\item Tests or performance measurements that interact with Grid services
require authentication and should be executed using a standard user GSI
credential that is mapped to the standard user account.

\item Tests or performance measurements should be executed locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

\item The configuration of tests or performance measurements should be managed
centrally in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

@@

\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
1~\cite{inca1} to implement a user-level Grid monitoring system that followed
the above guidelines.  At that time, the only available user-level Grid
monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
results in HTML.  Although these tools were easy to install and produced
useful information, they showed the view of the Grid from a single
resource, lacked automation, and were not easily extensible.  Inca 1 provided
the means to verify that CTSS was deployed consistently across all TeraGrid
resources and to monitor its status.

The initial
version of Inca was implemented as a client-server architecture.  It provided
data collection, data storage (accessible from a Web services interface and with 
limited archiving capabilities), and data display though Web status
pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
2003. Running Inca 1 for a year and a half on TeraGrid taught 
valuable lessons that have been incorporated into the design of Inca 2, our
current release.  Inca 2
contains a number of substantial improvements over Inca 1 with respect to
security, installation and maintenance, and storage capabilities.  Inca 2 has
been running on TeraGrid since November 2006, and in February 2007 a production
version of the software was released.  Currently, seven other Grids in the
U.S., Europe, and Australia use Inca 2.

@@

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) after logging it to the
'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema to report software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling Inca to download a
short-term proxy before running this reporter. (As discussed in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the DB schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these comparisons change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

@@

>>>>

% Complex means they are difficult to provide and maintain. Describe the
% stakeholders.   Monitoring is needed.
Providing and maintaining a stable infrastructure for these complex 
Grid systems poses challenges for both administrators who build and
maintain Grid resources and scientists who use them.  System
administration is distributed across multiple administrative domains 
requiring a significant amount of coordination.  This is typically performed by
a group of Grid administrators or operators who consider local site policies and
resource heterogeneity
and decide when software (including updates and patches) should be deployed to
resources and how it should be configured.  
Each site's system administrators, who are not necessarily Grid
experts, are then responsible for providing the required Grid software
components and services for their resource and debugging any problems that
arise.  Well-defined requirements and good communication are required in this
model.  Otherwise, inconsistencies arise between the resources that either
inconvenience the user or prevent them from using a particular resource
altogether.  A second challenge is that failures will occur over
time in the Grid services due to network or system failures, software
misconfiguration, or software bugs. 
Grid monitoring can be used to detect such problems, leading to a more
stable and dependable Grid infrastructure.

@@

\item User-level tests or performance measurements of the Grid infrastructure
should be run from a standard user
account in order to reflect regular user experiences.  It is important not to execute from a system administrator's account,
because it may have special privileges and use custom shell initialization files.

\item User-level tests or performance measurements that interact with Grid services
require authentication and should be executed using a standard user GSI
credential that is mapped to the standard user account.

\item User-level tests should be
written and configured using information directly from user documentation
(e.g., hostnames, ports, pathnames, etc.) to emulate a regular user.  
This may not always be possible
when documentation and testing are done in parallel in a pre-production
environment, but they should be closely coordinated activities.

\item The configuration of user-level tests or performance measurements should be managed
centrally in order to ensure consistent testing of the resources, rather than
by system administrators who may not use the same information that is
available to users.

@@

\item User-level tests or performance measurements should be executed locally on all Grid
resources when appropriate so that all Grid access points available to users
are verified.  Similarly, it is important to execute some tests all-to-all
in order to detect site-to-site configuration errors such as authentication
problems.

@@

\noindent In 2003 SDSC, in partnership with TeraGrid, began developing Inca
1~\cite{inca1} to implement a user-level Grid monitoring system that followed
the defined guidelines.  At that time, the only available user-level Grid
monitoring tools were the NCSA TestGrid script~\cite{ncsa-test} and
Grid Integration Test Script (GITS)~\cite{gits}, both of which ran a fixed number of Grid tests and formatted
results in HTML.  Although these tools were easy to install and produced
useful information, they showed the view of the Grid from a single
resource, lacked automation, and were not easily extensible.  Inca 1 provided
the means to verify the common user environment was deployed consistently across all TeraGrid
resources and monitored its status.

The initial
version of Inca was implemented as a client-server architecture.  It provided
data collection, data storage (accessible from a Web services interface and with 
limited archiving capabilities), and data display though Web status
pages.  Inca 1 was first deployed to TeraGrid in mid 2003 and released in late
2003. Running Inca 1 for a year and a half on TeraGrid taught 
valuable lessons that have been incorporated into the design of Inca 2, our
current release.  Inca 2
contains a number of substantial improvements over Inca 1 with respect to
security, installation and maintenance, and storage capabilities.  Inca 2 has
been running on TeraGrid since November 2006 and a production
version of the software was released in February 2007.  Currently, seven other Grids in the
U.S., Europe, and Australia use Inca 2.

@@

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) after logging it to the
'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema to report software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling Inca to download a
short-term proxy before running this reporter (as discussed in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

The Inca depot server is responsible for storing configuration information and
the data produced by reporters. The depot uses a relational database via
Hibernate~\cite{hibernate}, enabling the use of a variety of database backends.
The depot provides full archiving of reporter output, and the database schema is
tuned to minimize redundant data.  Inca administrators can specify comparison
tests to run on reports as they are received, and the depot will send email
when the results of these comparisons change.  This provides the administrator
with quick notification of problems as they appear and of the results of
repairs.

@@

This work was supported by the following NSF grants:  Cooperative Agreement
Award \#0503944 SCI: TeraGrid Resource Partners,
